\input{./preamble.tex}

\title{Journal}
\author{Aheer srabon}
\date{}

\begin{document}
\maketitle

\section{July 05, 2024}
\noindent I got admitted to BUET on February 22nd, 2020. It's more than four years now. I don't know
what I did in these four years, I really don't. But I must've done something, I can't really recall.
For as long as I can remember, I have always wanted to be a computer guy. I can't really call myself
a computer guy. I always wanted to be economically stable. I am not economically stable. I always wanted
a fit and strong body. My body is not as fit and strong I wished it to be. I loved one girl and couldn't
make her mine. It's 4:20 AM in the morning and I feel lost. I feel like a failure and a loser. I thought
about killing myself a while back. But soon realized that suicide is not the way out. Because, to my
knowledge, life is the only environment that I am familiar with. Now that suicide is out of the way
and I am not dying anytime soon, I must charge all the way up. If I can't change the changables, I am
inevitably going to feel worse.

\begin{itemize}
\itemsep0em
	\item Only source of entertainment are books, exercise and sleep.
	\item No one is ever going to do things for me.
\end{itemize}

\noindent Make the TODO, do the work, as simple as that. Don't blow it now, there is no time.

\section{July 09, 2024}
\noindent I was angry at her recently. I am never angry. I always knew that I am not a fully functional
human being like others. But recently, I am not aspiring power. Rather, I am upholding morality as way
to justify weakness (my weaknesses). I have been talking a lot and I have been angry. I am not like this.
I always esteemed greatness over anything. But nowadays, I am weak and pathetic. I don't want to be weak
and pathetic. Can I concretely say that today everything changes? Do I have the courage and strength?
I think I do.

\section{July 10, 2024}
\noindent I am fairly old now, 23 years to be specific. I peeked inside of myself quite a few times in all
these years. And I have seen things and changed things. But I don't think I have had the opportunity to
shape myself the way I want (not the way I should). Now, I don't want to be the person from \emph{Notes
from the underground}. I don't want to regret things, nor do I want to remain mediocre. This month, I am
going to cultivate habits that I want to cultivate. There are certain qualities that I deem superior,

\begin{itemize}
\itemsep0em
	\item Being a good mathematician.
	\item Earning a decent amount of money.
	\item Having a fit body.
	\item Coding and Machine Learning.
\end{itemize}

\noindent I ought to be able to \emph{concentrate for a long period of time} and must not \emph{give into
temptations}. Listing and writing down things, although being a pretty good method to practice, is not 
enough unless I incorporate the mental changes necessary.

\section{July 22, 2024}
\noindent I know I have told myself what I'm about to tell myself a great number of times. But today, it all
changes.

\section{August 13, 2024}
\noindent Okay, so another half a month passed and I did nothing. Same old story. I am such a piece of a shit.

\end{document}
