\input{./preamble.tex}

\title{Temporary}
\author{Aheer srabon}
\date{}

\begin{document}
\maketitle

\section{Debunking the Palestinian Lie}
\textbf{May 16, 2011: } The long overdue palestinian state by Mahmood Abbas. Abbas called for the
UN to formarly recognize a palestinian state based on the 1948 armistice lines (previously, the
arabs made it clear that these were simply ceasefire lines and didn't demarcate country boundaries)
regradless of negotiation with the state of Israel. Obama declared that Israel must agree to return
to the 1948 armistice borders modified only by mutually agreed landswaps. In Palestine, there is 
more than enough room for a prosperous Jewish state and a prosperous Arab state.

\textbf{After WWI ended,} with the dismantling of the ottoman empire, the league of nations established
the \textbf{Mandate for Palestine} including all of the land that is now Israel, the west bank and the
Gaza strip, plus the entire territory east of the jordan river (now called the kingdom of jordan). The
area under the mandate was as large as Syria and about half as large as Iraq, yet the total population
at that time was less than a million, of whom 10\% are Jews (who made Aliyah).

\noindent\textbf{Third Arab-Israeli War: } 


\textbf{Mandate for Palestine} was the vast, under-developed and under-populated territory that the
British promised in 1917 \textbf{Balfour Declaration}. \textbf{Balfour Declaration} supports the
establishment in Palestine of a national home for the Jewish people. It also states that nothing
shall be done which may prejudice the civil and religious rights of existing non-jewish communities
in Palestine. It further supported open jewish immigration, freedom of speech, religion and assembly.
Under the Turkish rule, Palestinians lacked all the above rights. The ottoman empire never recognize
Palestinians as possessing any national identity.

\textbf{The now-Palestinians} quickly took the advantage of freedom of speech, demanding to stop Jewish
immigration. During the Paris peace conference, one Arab representative said, ``We will push the zionists
into the sea, or they will send us back into the dessert''. \textbf{Aref Dajani}, a palestinian leader
from Jerusalem warned, "It is impossible to live with the Jews. In all the countries where they are at 
present, they are not wanted because they always arrive to suck the blood of everybody. If the league
of nations will not listen to the words of Arabs, this country will become a river of blood".

\noindent\textbf{Nebi Musa Riot: }

\noindent The now-Palestinian demand to stop Jewish immigration was not granted. And blood flowed. In April,
1920, Jerusalem was the first flashpoint for regular Arab attacks on Jewish communities. The now-palestinians
poured into the old city. The muslim mayor of Jerusalem and other notables worked up the crowd to 
launch a \textbf{Jihad} against the Jews. "We will drink the blood of the Jews". "Mohammad's religion was
born with the sword". 6 jews dead, hundreds beaten and widespread destruction of property. What became
knows as the \textbf{Nebi Musa Riot}, was the opening shot in a 90 year war to reverse the \textbf{Balfour
declaration}. The east of the jordan river was excluded out of the total area accessible to the Jews.
Now the Balfour declaration was carried out from the jordan river to meditorian sea, less space, more
hatred. It is important to note that during \textbf{Nebi Musa Riot}, there was no such thing as a palestinian.
It was mostly the collapse of the UAR in 1961, the humiliation and death of Gamal Abdel Nasser (the figurehead 
of pan-Arab nationalism), and the work of Yasser Arafat and his opposition to zionism that led to the modern
Palestinian national identity. There were many other riots against the Jews like the \textbf{Hebron massacre}
in the 1929. During the \textbf{Hebron massacre}, muslims killed 67 to 69 Jews on 24 August, 1929 in Hebron,
then part of Mandatory Palestine. Arabs incited this violence by rumors that Jews were planning to seize
control of the Temple Mount in Jerusalem.

\textbf{Haj Amin Al Husaini} was the grand mufti and president of the supreme muslim council. An endless
Jihad was declared against all the Jews by the Arab led by Husaini. The British sent a royal commision
to investigate a solution. The Jews pressed for a partition of the territory into two states, "even
if the territory assigned to the Jews was the size of a tablecloth". The peal commission's final report
published in July, 1937 proposed such a division. The Jews were offered an independent state in a small
enclave along the sea coast, from Tel Aviv to the north of the country, constituting about 20\% of the 
remaining mandate territory, while the Palestinian arabs would get 80\% for their own state. The Zionists
accepted the commision's partition plan. Led by the mufti, the arabs rejected the partition proposal and
pressed on with the armed revolt against the mandate. The British subdued the protest for a time and Husaini
was exiled to hitler's nazi Germany (special guest of the Fuhrer).

\textbf{After WWII}, Britain relinquished authority over the mandate. UN created yet another commision to
decide what to do with the contested territory. The commission recommended (7 to 3 vote), yet another
partition. This time both zionist and arabs would get about half of the existing territory. Zionists quickly
made public their acceptance of the proposal. But arabs once again refused to accept the proposal and
said that any partition would be met with rivers of blood.

\textbf{Shortly after the UN vote}, the 20 arab officials sent their newly organized \textbf{Arab Liberation
Army} against the Jews of the Palestine. Elements of five regular arab armies from Egypt, Jordan, Syria,
Iraq and Lebanon invaded Israel on May 15, 1948. \textbf{Abdul Rahman Azad} vowed that this will be a war of 
extermination and a momentous massacre which will be spoken of like the mongol massacres and the crusades.

\textbf{After a year of fighting}, it was the Jewish state had won a decisive victory. Based on \textbf{1949
Armistice Agreement}, Israels territory expanded by almost 40\%. For the second time in 10 years, arab leaders
rejected a partition plan that would have given them independence and more land designated for their state
than the Jewish state. Instead, they ended up with nothing. 650k palestinians became refugees.

\textbf{Jordan's king Abdullah}, sent his arab legion to occupy the palestinian west bank. Egypt took the Gaza
strip and for the next 18 years, denied palestinians any civil rights. It never occurred to the rulers of
Jordan or Egypt to create a state for the homeless palestinians. Palestinian leader never protested this
occupation of their land by foreign rulers.

\textbf{Three times} in the past decade, Israeli PMs have offered Palestinian leaders an independent state.
\textbf{At Camp-David} in 2000, Israeli PM Ahud Barack agreed to the borders suggested by president clinton that
would established a west bank gaza palestinian state with some territorial adjustments and with the palestinians
getting East Jerusalem as their capital. Palestinian Liberation Organization chairman \textbf{Yasser Arafat} 
walked out of negotiations and launched the \textbf{Second Intifada}. Three years of suicide bombing in Israel
followed.

\textbf{In 2005}, Israeli PM Ariel Chiron decided that it was against Israel's security interests to govern the
1.1 million palestinians in the Gaza strip. Chiron dismantled all of the Jewish settlements and pulled Israeli
forces back across the 1967 borders between Israel and Gaza without any land swaps. Israel also left a flower
export industry to the palestinians. The palestinians responded by first destroying the flower export industry
and then launched a war of missiles and rockets againsts civilian targets in Israel.

\textbf{In a September, 2008} meeting in Jerusalem, Israeli PM Ahud Olmert presented president Mahmood Abbas with
a detailed map of a future palestinian state that with land swaps would constitute close to 100\% of the territory
of the west bank of gaza prior to june 1967 war. Olmert also offered to divide Jerusalem enabling the palestinians
to locate their capital in the eastern half of the city. Abbas took the map but never returned. This was the last
time the Israeli and palestinian leaders met.

\textbf{Many times over the} last 63 years, both the international community and the Israeli community offered
the Arabs of palestine their own state. Each time, these offeres have been met by more violence against Jewish
citizens. Neither president Abbas nor president Obama are ignorant of this fact. 


\section{Random}
\noindent 2.122, 2.62 and 9.30, 3.85 contradicts.
\noindent 78.31 to 78.33 WTF? Full breasted virgins?
\noindent 54.1 no fucking way
\noindent 66.5 umar said.. whatever fuck it
\noindent Sahih Bukhari 4.52.60

\end{document}
