\input{../preamble.tex}

\title{AtCoder problems}
\author{Aheer Srabon}
\date{}

\begin{document}
	\maketitle

	\section{Atcoder Beginner Contest 347}
	\subsection{Task A - Divisible}
	\noindent \textbf{Problem Statement: } You are given positive
	integers $ N $ and $ K $, and a sequence of length $ N $.
	$ A = (A_1, A_2,...,A_N) $. Extract all elements of A that are
	multiples of $ K $, divide them by $ K $, and print the
	quotients.

	\vspace{1cm}

	\noindent \textbf{Solution: }
	\lstinputlisting[language=C++]{./ABC_347/A.cpp}

	\subsection{Task B - Substring}
	\noindent \textbf{Problem Statement: } You are given a string 
	S consisting of lowercase English letters. How many different 
	non-empty substrings does S have?
	A substring is a contiguous subsequence.
	For example, xxx is a substring of yxxxy but not of xxyxx.

	\vspace{1cm}

	\noindent \textbf{Solution: }
	\lstinputlisting[language=C++]{./ABC_347/B.cpp}

	\subsection{Task C - Ideal Holidays}
	\noindent \textbf{Problem statement: } In the kingdom of AtCoder,
	a week consists of $ A + B $ days, with the first through A-th
	days being holidays and the $ (A+1) $-th through $ (A+B) $-th
	being weekdays.

	\noindent Takahashi has $ N $ plans, and the $ i $-th plan is
	scheduled $ D_i $ days later.

	\noindent He has forgotten what day of the week it is today.
	Determine if it is possible for all of his $ N $ plans to be
	scheduled on holidays.

	\vspace{0.5cm}
	\noindent \textbf{Constraints: }
	\begin{itemize}
		\item $ 1 \leq N \leq 2\e{5} $
		\item $ 1 \leq A, B \leq \e{9} $
		\item $ 1 \leq D_1 < D_2 < \dots < D_N \leq \e{9} $
	\end{itemize}
	\vspace{0.5cm}
	\noindent \textbf{Solution: }
	\lstinputlisting[language=C++]{./ABC_347/C.cpp}

	\noindent The method lower\_bound(first, last, val) in C++ is used to return 
	an iterator pointing to the first element in the range [first, last) which has 
	value not less than val. So, the function returns an iterator pointing to the
	next smallest number just greater than or equal to that number. If there are multiple
	values that are equal to val, lower\_bound() returns the iterator of the first such
	value. It operates on \emph{sorted} vector. The first two arguments are iterators. The
	return value of lower\_bound() is an iterator to the 

	\section{Atcoder Regular Contest 175}
	\subsection{Task A - Spoon Taking Problem}

	\noindent \textbf{Solution: }
	\lstinputlisting[language=C++]{./ARC_175/A.cpp}



\end{document}
